mruby Bytecode Loader Using Bluetooth in Multi-VM Environment

### 2016-02-22 thesis/thesis.tex
update

\begin{abstract}
In recent years, the productivity of embedded systems has become a problem due to their complexity and large-scale.
For the purpose of improving the productivity for embedded software development, the mruby on TECS framework has been proposed that is applied mruby (Lightweight Ruby) and supports component-based development.
In the current mruby on TECS, the mruby programs have to be compiled and linked every time the programs are modified because the mruby bytecodes are incorporated in the platform.
Moreover, while the framework supports multi-VM, developers need to be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs in concurrent or/and parallel.
To improve the development efficiency, this paper proposes an mruby bytecode loader using Bluetooth as an extension of mruby on TECS.
The loader executes two mruby bytecodes, mruby application bytecode and mruby library bytecode.
mruby application bytecode modified frequently is sent from a host to a target device by developers.
mruby library bytecode modified infrequently is preserved beforehand with the platform in a storage/ROM device at the time of the first compilation.
In addition, multiple mruby programs cooperatively run in the proposed framework.
A RiteVM sceduler makes multitasking processing more easy-to-use than that of mruby on TECS.
Synchronization of starting multiple tasks is also implemented with Eventflag. 
Experimental results demonstrate the advantages of the proposed framework.
\end{abstract}
\clearpage
\tableofcontents
\clearpage
\setcounter{page}{0}
\pagenumbering{arabic}
\chapter{Introduction}
In these days, embedded systems have been required the high-quality and the high-performance.
Due to this trend, the complexity of embedded systems also increases and the scale is larger.
For example, IoT (Internet of Things) applications.
The low production cost and the short developing period of time are also needed.

@@

%This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and RiteVM sceduler.
mruby on TECS has several problems at present.
One of the problems is low software development efficiency.
mruby on TECS only supports a storage/ROM device in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3} to load mruby programs.
For example, an SD card should be inserted and pulled out repeatedly, or a ROM should be rewritten if mruby programs are modified.
Developers should also restart an OS on a target device.
%Moreover, in the current system if developers attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks do not run unless developers call the OS's function.
%In addition developers must prepare as many VMs as the number of tasks because one RiteVM supports only one task.
Moreover, although mruby on TECS has supported the multi-VM, developers need to call OS's function in order to execute multiple tasks.
These problem are a big burden on developers.

This paper proposes an extended framework of mruby on TECS: an mruby bytecode loader using Bluetooth and a RiteVM scheduler for fairly executing mruby programs.
To improve the development efficiency, the mruby bytecode loader using Bluetooth enables developers to write the platform in a strage device only once at the beginning and to transfer mruby application codes from a host to a target device.
The RiteVM scheuler enables developers to run multitasking programs more easily than mruby on TECS.
%Specifically, a cyclic handler of switching tasks is implemented.
%This paper evaluates the proposed framework in term of data transfer rate, overhead of cyclic handler and execution time.

{\bf Contribution}: The proposed framework gives the contribution in the following points.
\begin{enumerate}
\item {\bf To improve the software development efficiency:} Developers do not need to rewrite a storage/ROM device and also to restart an OS.
The loader supports the countinuous loading, which saves the Bluetooth set-up time.
Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
\item {\bf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM sceduler switches tasks cyclically.
In additon, synchronization of multiple tasks is also implemented.
\item {\bf To focus on the benefits of component-based developments:} This paper shows the specific examples for the benefits of component-based development. 
\end{enumerate}

@@

\subsection{Component Model}\mbox{}\\

@@

\subsection{Component Description}\mbox{}\\

@@

\subsection{System Model}\mbox{}\\

@@

\subsection{mruby-TECS Bridge}\mbox{}\\

@@

\chapter{Design and Implementation}
\label{sec:Design and Implementation}
Figure \ref{fig:system_model} shows the detailed system model of the proposed framework.
Each mruby application bytecode transferred from the host is received by the loader in the RiteVM.
The RiteVM reads the own bytecode and executes it.
The mruby applications run at the same time because of synchronization processing.
The RiteVM scheuler switches tasks as multiple tasks can run in concurrent.

@@

mruby programs are consisted of mruby application and libraries.
mruby application is the main code, which developers should program.
mruby libraries are the codes defining the functions for application such as Ruby classes. 
The mruby bytecodes including mruby application and libraries can be sent and run.
However, it is also wasteful in terms of the size and time to send because libraries are not frequently modified. 
The proposed framework provides the design that only mruby applications are sent and mruby libraries are preserved with the platform in the storage/ROM device beforehand.
Due to this design, RiteVMs can share the mruby libraries.
In additon, a RiteVM can use the own library that other RiteVMs should not use.

@@

\subsection{Component of RiteVM with mruby bytecode loader using Bluetooth} \mbox{}\\

@@

As an approach for multitask processing, the proposed framework provides the RiteVM scheuler which is a fair scheduler and runs multiple tasks equally.
The RiteVM scheuler is utilized only when application tasks have the same priority.
mruby applications can run in concurrent without developers calling the OS's function.
The application programs can also utilize the existing programs since the structures of the programs are not changed.

\subsection{RiteVM Scheduler} \mbox{}\\

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{../EMSOFT2016/figure/rotateReadyQueue.pdf}
    \caption{The design of RiteVM sceduler}
    \label{fig:rotateReadyQueue}
\end{figure}

\subsection{Component of RiteVM Scheduler} \mbox{}\\

@@

\subsection{Synchronization of Multiple RiteVM Tasks} \mbox{}\\

@@

In the framework, RiteVMs, the RiteVM scheuler, and Eventflag are implemented as components.
Therefore, developers can easily add or remove these components and also reuse them.
For example, if developers do not need the RiteVM scheuler, the .cdl files shown as Figures \ref{celltype_cyclic_handler} and \ref{build_cyclic_handler} should be commented out such as {\it //import($<$tRiteVMScheduler.cdl$>$);}.
This advantage of CBD saves developers the labor of rewriting a kernel configuration file.

In additon, the code size can desrease by developing with component-based. 
In the proposed framework, the advantage is applied in the Eventflag component.
The set pattern and wait pattern are defined as attributes of the component as shown in Figure \ref{fig:Eventflag} (B).
This design such as {\it cEventflag\_set(ATTR\_setPattern)} enables the program without ``if" statements and reuses the identical .c file.
Developers do not need to modify the .c file because the .cdl files are prepared in accordance with the number of RiteVMs
In additon, the components of Eventflag are built with {\it [optional]} in TECS.
{\it [optional]} means that the codes are run only when the call port is connected.
The .c file does not be rewritten even if developers do not use Eventflag.

@@

The comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
The 100,000 times loop program is used as mruby application for evaluation of execution time.
In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.
In Figure \ref{fig:comparison_s_c_m}, the cyclic time of the cyclic handler for multitasking is one msec.
%While multitask's execution time is slower than singletask's, co-routine takes more time than multitask to execute an mruby application.
This result shows the proposed design is superior to co-routine in terms of execution time.
Moreover, developers can utilize the scheuler practically because the overhead of the RiteVM scheuler is about 5 \%.
Switching tasks' overhead is also evaluated, that is about three $\mu$sec on average.
%The number of switching tasks is from 500 to 600 because singletasking process in Figure \ref{fig:comparison_s_c_m} takes about 540 msec.
%Therefore, the overhead of multitasking is 0.5 \% or less, and multitasking can be used without the overhead.
The scheuler interrupts and switches tasks, which causes this overhead.

@@

Figure \ref{fig:comparison_msec} shows the execution time of multitasking with the cyclic handler.
A lower limit of the cyclic time is one msec due to the specification of TOPPERS/HRP2, the used RTOS.
More than eight msec do not be evaluated in this paper because it is thought the larger cyclic time influences applications.
%Each execution time of cyclic period is the same as the others.
%That is because the overhead of switching tasks (about 3 $\mu$sec) is small in comparison with the execution time.
The execution time decreases as the cyclic time become larger, because the number of switching tasks decreases.
The execution time of one msec is only about 1 \% lager than that of eight msec.
The RiteVM scheuler with small cyclic time can effectively execute multiple tasks because the cyclic time overhead is not large.
%This results also shows the overhead becomes smaller as the cyclic time is larger, because the overhead depends on the number of switching tasks.
%The smaller cyclic time is better in multitasking due to concurrent and/or parallel processing.

@@

To indicate the superior of component-based development, the comparison of code lines between two .c files is shown in Table \ref{tab:codesize}.
(A) and (B) mean the source files in the upper and lower of Figure \ref{fig:Eventflag}, respectively. 
In terms of .c, (B)'s lines do not increase even if the number of RiteVMs increases, while (A)'s lines increase as the number increases.
(B)'s .c file can be utilized without modification, regardless of the number of RiteVMs.
Moreover, lines of two .cdl files are equal.
The skillfull component-based development brings this advantages such as the decrease of code lines and non-modified code, which leads high productivity and high maintainability.

\begin{table}[t]
    \centering
    \caption{Lines of .c and .cdl file for the number of RiteVM}
    \begin{tabular}{c||cc|c}
                & (A)       & (B)     & Diff  \\ \hline
        .c (Total)      & 8$\times$$\alpha$$+$134  & 130     & 8$\times$$\alpha+$4\\
        .c (Modified)   & 10$\times\alpha$$-$2 & 0   &  10$\times\alpha$$-$2 \\
        .cdl    & 18$\times$$\alpha$$+$25   & 18$\times$$\alpha$$+$25 & 0     \\
        \multicolumn{3}{l}{{\small $\alpha$} : {\scriptsize the number of RiteVM}}
    \end{tabular}
    \label{tab:codesize}
\end{table}

@@

python-on-a-chip (p14p) is a Python run-time system that uses a reduced Python VM called PyMite.
The VM runs a significant subset of Python language with few resources on a microcontroller.
p14p can run multiple stackless green threads.

The Owl system is an embedded Python run-time system.
The Owl is a complete system for ARM Cortex-M3 microcontrollers.
The Owl toolchain produces relocatable memory images, that are directly runnable on the microcontroller, from Python code objects.
The interpreter of the Owl system is the same as that of python-on-a-chip.

@@

Table \ref{tab:comparison} shows a comparison between the proposed framework and previous work.
The proposed framework supports the loader, the VM scheuler, and synchronization of application.
\begin{landscape}
\begin{table}[t]
    \centering
    \caption{Comparion of the proposed and previous work}
    \footnotesize
    \begin{tabular}{c||c|ccccccc}
        & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & VM Managenment & VM Scheduler & \shortstack{Synchronization of\\Application} & Co-routine \\ \hline
        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            & \checkmark \\
        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &             &            & \checkmark \\
        eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            & \checkmark \\
        mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            & \checkmark \\
        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark & 			   &            & \checkmark \\
        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark \\
    \end{tabular}
    \label{tab:comparison}
\end{table}
\end{landscape}

\chapter{Conclusion}
\label{sec:Conclusion}
This paper has presented an extended framework of mruby on TECS: mruby bytecode loader using Bluetooth and RiteVM scheuler.
The loader provides developers with the software development efficiency without rewriting a storage/ROM device and restarting an OS.
The proposed framework can be applied to many kinds of embedded systems  because the loader can use not only Bluetooth also wired serial connection.
%Thus, the proposed framework can be utilized on the deveces without Bluetooth.
The RiteVM scheuler makes multitasking more easily than the current mruby on TECS.
In the evaluation, experimental results of the loader and the RiteVM scheduler show their advantages.
The loader can improve the software development efficiency on mruby on TECS.
The RiteVM sceduler has the effectiveness in terms of execution time and ease of use compared with singletasking and co-routine.
%because of the low overhead.

The proposed framework is developed in component-base by TECS.
The facilities such as RiteVMs, the RiteVM scheuler, and Eventflag are implemented as components.
Therefore, developers can easily add or remove the functionalities as necessary, and also reuse them.
Developers can choose fair scheduling or fixed-priority scheduling since the RiteVM scheuler can be easily removed.
Component-based development can increase productivity.

In the future, the mruby bytecode loader using Bluetooth will be supported to handle multiple bytecodes and run the application in multi-VM.
Moreover, the .cdl files for RiteVM and mruby-TECS bridge are generated automatically using a plugin, and developers can send a bytecode with ZMODEM protocol on the command line.

>>>>

\begin{abstract}
In recent years, the productivity of embedded systems has become a problem due to their complexity and large-scale.
For the purpose of improving the productivity for embedded software development, the mruby on TECS framework has been proposed that is applied mruby (Lightweight Ruby) and supports component-based development.
In the current mruby on TECS, the mruby programs have to be compiled and linked every time the programs are modified because the mruby bytecodes are incorporated in the platform.
Moreover, while the framework supports multi-VM, developers need to be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs in concurrent or/and parallel.
To improve the development efficiency, this paper proposes an mruby bytecode loader using Bluetooth as an extension of mruby on TECS.
The loader executes two mruby bytecodes, mruby application bytecode and mruby library bytecode.
mruby application bytecode modified frequently is sent from a host to a target device by developers.
mruby library bytecode modified infrequently is preserved beforehand with the platform in a storage/ROM device at the time of the first compilation.
In addition, multiple mruby programs cooperatively run in the proposed framework.
A RiteVM scheduler makes multitasking processing more easy-to-use than that of mruby on TECS.
Synchronization of starting multiple tasks is also implemented with Eventflag. 
Experimental results demonstrate the advantages of the proposed framework.
\end{abstract}
\clearpage
\tableofcontents
\clearpage
\setcounter{page}{0}
\pagenumbering{arabic}
\chapter{Introduction}
In these days, embedded systems have been required the high-quality and the high-performance.
Due to this trend, the complexity of embedded systems also increases and the scale is larger.
For example, IoT (Internet of Things) applications.
The low production cost and the short developing period of time are also needed.

@@

%This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and RiteVM scheduler.
mruby on TECS has several problems at present.
One of the problems is low software development efficiency.
mruby on TECS only supports a storage/ROM device in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3} to load mruby programs.
For example, an SD card should be inserted and pulled out repeatedly, or a ROM should be rewritten if mruby programs are modified.
Developers should also restart an OS on a target device.
%Moreover, in the current system if developers attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks do not run unless developers call the OS's function.
%In addition developers must prepare as many VMs as the number of tasks because one RiteVM supports only one task.
Moreover, although mruby on TECS has supported the multi-VM, developers need to call OS's function in order to execute multiple tasks.
These problem are a big burden on developers.

This paper proposes an extended framework of mruby on TECS: an mruby bytecode loader using Bluetooth and a RiteVM scheduler for fairly executing mruby programs.
To improve the development efficiency, the mruby bytecode loader using Bluetooth enables developers to write the platform in a storage device only once at the beginning and to transfer mruby application codes from a host to a target device.
The RiteVM scheduler enables developers to run multitasking programs more easily than mruby on TECS.
%Specifically, a cyclic handler of switching tasks is implemented.
%This paper evaluates the proposed framework in term of data transfer rate, overhead of cyclic handler and execution time.

{\bf Contribution}: The proposed framework gives the contribution in the following points.
\begin{enumerate}
\item {\bf To improve the software development efficiency:} Developers do not need to rewrite a storage/ROM device and also to restart an OS.
The loader supports the continuous loading, which saves the Bluetooth set-up time.
Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
\item {\bf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM scheduler switches tasks cyclically.
In addition, synchronization of multiple tasks is also implemented.
\item {\bf To focus on the benefits of component-based developments:} This paper shows the specific examples for the benefits of component-based development. 
\end{enumerate}

@@

\subsection{Component Model}

@@

\subsection{Component Description}

@@

\subsection{System Model}

@@

\subsection{mruby-TECS Bridge}

@@

\chapter{Design and Implementation}
\label{sec:Design and Implementation}
Figure \ref{fig:system_model} shows the detailed system model of the proposed framework.
Each mruby application bytecode transferred from the host is received by the loader in the RiteVM.
The RiteVM reads the own bytecode and executes it.
The mruby applications run at the same time because of synchronization processing.
The RiteVM scheduler switches tasks as multiple tasks can run in concurrent.

@@

mruby programs are consisted of mruby application and libraries.
mruby application is the main code, which developers should program.
mruby libraries are the codes defining the functions for application such as Ruby classes. 
The mruby bytecodes including mruby application and libraries can be sent and run.
However, it is also wasteful in terms of the size and time to send because libraries are not frequently modified. 
The proposed framework provides the design that only mruby applications are sent and mruby libraries are preserved with the platform in the storage/ROM device beforehand.
Due to this design, RiteVMs can share the mruby libraries.
In addition, a RiteVM can use the own library that other RiteVMs should not use.

@@

\subsection{Component of RiteVM with mruby bytecode loader using Bluetooth}

@@

As an approach for multitask processing, the proposed framework provides the RiteVM scheduler which is a fair scheduler and runs multiple tasks equally.
The RiteVM scheduler is utilized only when application tasks have the same priority.
mruby applications can run in concurrent without developers calling the OS's function.
The application programs can also utilize the existing programs since the structures of the programs are not changed.

\subsection{RiteVM Scheduler}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{../EMSOFT2016/figure/rotateReadyQueue.pdf}
    \caption{The design of RiteVM scheduler}
    \label{fig:rotateReadyQueue}
\end{figure}

\subsection{Component of RiteVM Scheduler}

@@

\subsection{Synchronization of Multiple RiteVM Tasks}

@@

In the framework, RiteVMs, the RiteVM scheduler, and Eventflag are implemented as components.
Therefore, developers can easily add or remove these components and also reuse them.
For example, if developers do not need the RiteVM scheduler, the .cdl files shown as Figures \ref{celltype_cyclic_handler} and \ref{build_cyclic_handler} should be commented out such as {\it //import($<$tRiteVMScheduler.cdl$>$);}.
This advantage of CBD saves developers the labor of rewriting a kernel configuration file.

In addition, the code size can decrease by developing with component-based. 
In the proposed framework, the advantage is applied in the Eventflag component.
The set pattern and wait pattern are defined as attributes of the component as shown in Figure \ref{fig:Eventflag} (B).
This design such as {\it cEventflag\_set(ATTR\_setPattern)} enables the program without ``if" statements and reuses the identical .c file.
Developers do not need to modify the .c file because the .cdl files are prepared in accordance with the number of RiteVMs
In addition, the components of Eventflag are built with {\it [optional]} in TECS.
{\it [optional]} means that the codes are run only when the call port is connected.
The .c file does not be rewritten even if developers do not use Eventflag.

@@

The comparison of the application execution time with singletasking, co-routine, and multitasking is shown in Figure \ref{fig:comparison_s_c_m}.
The 100,000 times loop program is used as mruby application for evaluation of execution time.
In detail, the singletask program loops 100,000 times, and the multitask and co-routine programs loop 50,000 times in each task.
In Figure \ref{fig:comparison_s_c_m}, the cyclic time of the cyclic handler for multitasking is one msec.
%While multitask's execution time is slower than singletask's, co-routine takes more time than multitask to execute an mruby application.
This result shows the proposed design is superior to co-routine in terms of execution time.
Moreover, developers can utilize the scheduler practically because the overhead of the RiteVM scheduler is about 5 \%.
Switching tasks' overhead is also evaluated, that is about three $\mu$sec on average.
%The number of switching tasks is from 500 to 600 because singletasking process in Figure \ref{fig:comparison_s_c_m} takes about 540 msec.
%Therefore, the overhead of multitasking is 0.5 \% or less, and multitasking can be used without the overhead.
The scheduler interrupts and switches tasks, which causes this overhead.

@@

Figure \ref{fig:comparison_msec} shows the execution time of multitasking with the cyclic handler.
A lower limit of the cyclic time is one msec due to the specification of TOPPERS/HRP2, the used RTOS.
More than eight msec do not be evaluated in this paper because it is thought the larger cyclic time influences applications.
%Each execution time of cyclic period is the same as the others.
%That is because the overhead of switching tasks (about 3 $\mu$sec) is small in comparison with the execution time.
The execution time decreases as the cyclic time become larger, because the number of switching tasks decreases.
The execution time of one msec is only about 1 \% lager than that of eight msec.
The RiteVM scheduler with small cyclic time can effectively execute multiple tasks because the cyclic time overhead is not large.
%This results also shows the overhead becomes smaller as the cyclic time is larger, because the overhead depends on the number of switching tasks.
%The smaller cyclic time is better in multitasking due to concurrent and/or parallel processing.

@@

To indicate the superior of component-based development, the comparison of code lines between two .c files is shown in Table \ref{tab:codesize}.
(A) and (B) mean the source files in the upper and lower of Figure \ref{fig:Eventflag}, respectively. 
In terms of .c, (B)'s lines do not increase even if the number of RiteVMs increases, while (A)'s lines increase as the number increases.
(B)'s .c file can be utilized without modification, regardless of the number of RiteVMs.
Moreover, lines of two .cdl files are equal.
The skillful component-based development brings this advantages such as the decrease of code lines and non-modified code, which leads high productivity and high maintainability.

\begin{table}[t]
    \centering
    \caption{Lines of .c and .cdl file for the number of RiteVM}
    \begin{tabular}{c||cc|c}
                & (A)       & (B)     & Diff  \\ \hline
        .c (Total)      & 8$\times$$\alpha$$+$134  & 130     & 8$\times$$\alpha+$4\\
        .c (Modification)   & 10$\times\alpha$$-$2 & 0   &  10$\times\alpha$$-$2 \\
        .cdl    & 18$\times$$\alpha$$+$25   & 18$\times$$\alpha$$+$25 & 0     \\
        \multicolumn{3}{l}{{\small $\alpha$} : {\scriptsize the number of RiteVM}}
    \end{tabular}
    \label{tab:codesize}
\end{table}

@@

python-on-a-chip (p14p) is a Python run-time system that uses a reduced Python VM called PyMite.
The VM runs a significant subset of Python language with few resources on a micro-controller.
p14p can run multiple stackless green threads.

The Owl system is an embedded Python run-time system.
The Owl is a complete system for ARM Cortex-M3 micro-controllers.
The Owl toolchain produces relocatable memory images, that are directly runnable on the micro-controller, from Python code objects.
The interpreter of the Owl system is the same as that of python-on-a-chip.

@@

Table \ref{tab:comparison} shows a comparison between the proposed framework and previous work.
The proposed framework supports the loader, the VM scheduler, and synchronization of application.
\begin{landscape}
\begin{table}[t]
    \centering
    \caption{Comparison of the proposed and previous work}
    \footnotesize
    \begin{tabular}{c||c|ccccccc}
        & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & VM Management & VM Scheduler & \shortstack{Synchronization of\\Application} & Co-routine \\ \hline
        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            & \checkmark \\
        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &             &            & \checkmark \\
        eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            & \checkmark \\
        mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            & \checkmark \\
        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark & 			   &            & \checkmark \\
        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark \\
    \end{tabular}
    \label{tab:comparison}
\end{table}
\end{landscape}

\chapter{Conclusion}
\label{sec:Conclusion}
This paper has presented an extended framework of mruby on TECS: mruby bytecode loader using Bluetooth and RiteVM scheduler.
The loader provides developers with the software development efficiency without rewriting a storage/ROM device and restarting an OS.
The proposed framework can be applied to many kinds of embedded systems  because the loader can use not only Bluetooth also wired serial connection.
%Thus, the proposed framework can be utilized on the devices without Bluetooth.
The RiteVM scheduler makes multitasking more easily than the current mruby on TECS.
In the evaluation, experimental results of the loader and the RiteVM scheduler show their advantages.
The loader can improve the software development efficiency on mruby on TECS.
The RiteVM scheduler has the effectiveness in terms of execution time and ease of use compared with singletasking and co-routine.
%because of the low overhead.

The proposed framework is developed in component-base by TECS.
The facilities such as RiteVMs, the RiteVM scheduler, and Eventflag are implemented as components.
Therefore, developers can easily add or remove the functionalities as necessary, and also reuse them.
Developers can choose fair scheduling or fixed-priority scheduling since the RiteVM scheduler can be easily removed.
Component-based development can increase productivity.

In the future, the mruby bytecode loader using Bluetooth will be supported to handle multiple bytecodes and run the application in multi-VM.
%Moreover, the .cdl files for RiteVM and mruby-TECS bridge are generated automatically using a plugin, and developers can send a bytecode with ZMODEM protocol on the command line.
Moreover, synchronization functionality between the RiteVMs will be proposed, and developers can send a bytecode with ZMODEM protocol on the commend line.
